%This is the acknowledgments tex file

%UF 
First, I would like to thank my advisor, Jaco Konigsberg, for giving me his support, encouragement and advice since the very beginning of my doctoral studies. I want to thank the University of Florida CMS group members that have accompanied me throughout these years. I am especially grateful with Luca Cadamuro, the HH guru, for his constant guidance, patience, teaching, and friendship. Moreover, I would like to thank Darin Acosta for his kind help and advice while I was based at CERN. I also want to thank the members of my dissertation committee for their review of this work and insightful discussions: Darin Acosta, Andrey Korytov, Konstantin Matchev and Arunava Banerjee. 

%FNAL and CERN people
I thank the University of Florida, the Fermilab LHC Physics Center (LPC), and the U.S. Department of Energy for their support to make this research possible. I would like to thank the CMS Analysis Review members for their comments and approving the result for the public: Maurizio Pierini, Nadya Chernyavskaya, Silvio Donato, Devdatta Majumder, and Don Lincoln. There are also several brilliant people who have helped along the way while working on my Ph.D. research. Special thanks go to Caterina Vernieri, Fabio Ravera, Vladimir Rekovic, Anadi Canepa, Maria Cepeda, Chris Palmer, Mia Liu, Sergo Jindariani, Jia Fu Low, and Javier Duarte. I would like to thank friends and colleagues who enriched my time at UF, Fermilab and CERN: Vladimir Martinez, Atul Divakarla, Jake Rosenzweig, Suzanne Rosenzweig, Jorge Martinez, Osvaldo Miguel, Chad Freer, Xunwu Zuo, Antonio di Maria, Daniel Guest, Andres Delanoy, Raffaele Gerosa, Elisa Fontanesi, Deborah Pinna, and Camilla Galloni. I would also like to thank my undergraduate advisors, Edgar Carrera and Francisco Yumiceva, for their support through my career as a particle physicist.

%Family, friends and Michelle
Lastly, I would like to thank my family. I will always be grateful to my parents Fernando and Janet and my sister Nicole, for their endless encouragement, trust, love and cheers through these years living abroad. I would also like to thank the Williams family for making me a part of the family. And Michelle, thank you for being my source of support, love and inspiration.