Daniel Fernando Guerrero Ibarra was born in Quito, Ecuador on November 29th, 1991. He lived most of his childhood and teenage years in a small town at the heart of the Ecuadorian coast called Quevedo. After finishing high school, he moved back to Quito to pursue a career in science at Escuela Polit$\mathrm{\acute{e}}$cnica Nacional, where he enrolled in the physics program. As an undergraduate student, he had the unique opportunity to engage early on in experimental particle physics research in the CMS experiment with the supervision and mentorship of Prof. Edgar Carrera and Prof. Francisco Yumiceva. During this time, he pursued his research in top quark physics and studies on hadron calorimeters at the CMS experiment by visiting the CERN Laboratory in Geneva, Switzerland, and the LHC Physics Center (LPC) at Fermilab in Chicago, IL. After obtaining his bachelor's degree, he joined the Physics Department at the University of Florida to pursue a doctorate focused on experimental high energy physics at the CMS experiment under the supervision of Prof. Jacobo Konigsberg. After finishing his coursework, he moved to CERN for two years where he was involved in the operations of the L1 trigger, and investigated the areas of the trigger upgrades and searches for Higgs boson pair production. During his final year, he completed his data analysis and trigger research through the prestigious Fermilab LPC Graduate Scholar award. He received a Doctorate of Philosophy in Physics at the University of Florida in the fall of 2021.